Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-13 hscc2017/paper.tex
hscc17
work on text

\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantization}

@@

Modern implementations of embedded control systems have proliferated with the
availability of low-cost devices that can perform highly non-trivial control
tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}.
Correct control is non-trivial, however. The problem is exacerbated by
artefacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization, and quantization noise
introduced by A/D and D/A conversion.  Thus, the programming is a key
barrier to broad adoption of digital control, and requires considerable
expertise.

Beyond classical a-posteriori validation procedures in digital control,
there has been plenty of previous work aiming at \emph{verifying} a given
controller designed by the engineer.  Recent work can show the stability of
digital controllers with consideration of implementation aspects, i.e.,
fixed-point arithmetic and the word length used~\cite{Bessa16}.  The authors
of~\cite{Bessa16} exploit advances in bit-accurate verification of C
programs to obtain a verifier for software-implemented digital control.

By contrast, we leverage a very recent step-change in the scalability of
\emph{program synthesis}.  Program synthesis engines use a program
specification as the starting point, and subsequently generate a sequence of
candidate programs.  The candidate programs are iteratively refined to match
the specification more closely.  Program synthesizers that implement
Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} are now
able to generate programs for highly non-trivial specifications with a very
high degree of automation.  Modern synthesis engines combine automated
testing, genetic algorithms and SMT-based automated
reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:journals/corr/AlurFSS16a}.

@@

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain,
%
$$
\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j}, \text{ that is } \tilde C(z) \equiv C(z). 
$$
%
However, given a real plant $\hat{G}(z)$, and a discretizing function
%
\begin{align}
\small
\label{FWL_tf}
\mathcal{F}&\langle I_p,F_p \rangle : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle\\
&\triangleq \tilde x = \mathcal{F}\langle I_p,F_p \rangle(x) : \tilde x=x-(x\bmod\tilde x)\nonumber\\
\mathcal{F}_n&\langle I_p,F_p \rangle(P \in \mathcal{P}) \\
&=\tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=\mathcal{F}\langle I_p,F_p \rangle(c_i)  \nonumber
\end{align}
%
we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\langle I_p,F_p \rangle(\hat{G}(z))$, where 
%
\begin{align}
% \label{digital_controller_tf}
% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_b \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
%
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
\vec{\tilde G} &=\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
\end{align}
%
where $\Delta_b\hat{c}_i=\hat{c}_i\bmod \tilde{c}_i$, 
and $\Delta_b{G}$ represents the plant uncertainty caused by
the rounding off effect.  We encompass all the uncertainty as
$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
%
As the cost of SAT solving increases with in the size of the problem
instance, our algorithm tries to solve the problem first for small $I_p$,
$F_p$, iteratively increasing the precision if it is insufficient.

>>>>

\keywords{Digital control synthesis, CEGIS, finite-word-length representation, time sampling, quantization}

@@

Modern implementations of embedded control systems have proliferated with the
availability of low-cost devices that can perform highly non-trivial control
tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}. 
Correct control is non-trivial, however. The problem is exacerbated by
artefacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization, and quantization noise
introduced by A/D and D/A conversion.  Thus, programming expertise is a key 
barrier to broad adoption of correct digital controllers, and requires considerable
knowledge often unusual to the control engineer.

Beyond classical a-posteriori validation procedures in digital control,
there has been plenty of previous work aiming at \emph{verifying} a given 
designed controller, which however broadly lack automation.  
Recent work has studied the stability of digital controllers with consideration of their implementation aspects, i.e.,
fixed-point arithmetic and the word length used: 
\cite{Bessa16} exploit advances in bit-accurate verification of C
programs to obtain a verifier for software-implemented digital control.

By contrast, we leverage a very recent step-change in the scalability of
\emph{program synthesis}.  Program synthesis engines use a program
specification as the starting point, and subsequently generate a sequence of
candidate programs from a given template.  
The candidate programs are iteratively refined to eventually match the desired program specification.   
Program synthesizers implementing the 
Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture are now
able to generate programs for highly non-trivial specifications with a very 
high degree of automation.  Modern synthesis engines combine automated testing, 
genetic algorithms, 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,DBLP:conf/lpar/DavidKL15}.

@@

Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
domain, 
\red{[confusing? (related to observation above.)]}
%
$$
\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j}, \text{ that is } \tilde C(z) \equiv C(z). 
$$
%
However, given a real plant $\hat{G}(z)$, and a discretizing function 
\red{[the function has been defined over a space of polynomials, but it is now applied to a real number x? ]}
%
\begin{align}
\small
%\label{FWL_tf}
\mathcal{F}&\langle I_p,F_p \rangle : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle\\
&\triangleq \tilde x = \mathcal{F}\langle I_p,F_p \rangle(x) : \tilde x=x-(x\bmod\tilde x)\nonumber\\ 
\red{\text{above: circular definition?}}\\
\mathcal{F}_n&\langle I_p,F_p \rangle(P \in \mathcal{P}) \\
&=\tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=\mathcal{F}\langle I_p,F_p \rangle(c_i)  \nonumber
\end{align}
%
we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\langle I_p,F_p \rangle(\hat{G}(z))$, where 
%
\begin{align}
% \label{digital_controller_tf}
% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_b \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
%
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
\vec{\tilde G} &=\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
\end{align}
%
where $\Delta_b\hat{c}_i=\hat{c}_i\bmod \tilde{c}_i$, 
and $\Delta_b{G}$ represents the plant uncertainty caused by
the rounding off effect.  We encompass all the uncertainty as
$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
%
As the cost of SAT solving increases with in the size of the problem
instance, our algorithm tries to solve the problem first for small $I_p$,
$F_p$, iteratively increasing the precision if it is insufficient.
